---
title: "Exercise 7"
author: "Yalin Yang"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: TRUE
    toc_float: TRUE
  word_document:
    toc: no
    toc_depth: '3'
---

# Try out the power of tidyverse

```{r message=FALSE}
# install.packages("tidyverse")
library(tidyverse)
# install.packages("rvest")
library(rvest)
```


## Import data

Use read.csv() Read and create a new dataset using following API links:
US county data (https://bit.ly/3gZKFve)[https://bit.ly/3gZKFve]
US state data (https://bit.ly/30dEWLB)[https://bit.ly/30dEWLB]

```{r}
url = 'https://bit.ly/3gZKFve'
df_us_contry <- read.csv(url)
url1 = 'https://bit.ly/30dEWLB'
df_us_state = read.csv(url1)
```

## Visualize

Create simple plots from each dataset

```{r fig.height=6, fig.width=9, message=FALSE}
df_us_state %>%
  group_by(state) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(desc(total_cases),state)%>%
  head(15) %>%
  ggplot() +  geom_bar(aes(x = total_cases, y = state),stat='identity')

```

```{r fig.height=6, fig.width=9, message=FALSE}
df_us_contry %>%
  group_by(date) %>%
  summarise(total_deaths = sum(deaths)) %>%
  ggplot(aes(x = as.Date(date), y = total_deaths, group=1)) +
  geom_line() +scale_x_date(date_labels = "%m-%Y")
```

## Collect data

Use `rvest()` to scrape the Wikipedia data table List of countries by external debt (https://bit.ly/2DCvmdt)[https://bit.ly/2DCvmdt]

```{r}
url2 = 'https://bit.ly/2DCvmdt'
df_wiki <- read_html(url2)

wiki_table <- df_wiki %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[1]') %>%
  html_table()

my_table = wiki_table[[1]]
names(my_table) <- c("Rank", "Country", "External debt", "Date", "Per capita",'% of GDP')
head(my_table)
```

## Clean up data

Make variables ready for analysis
* Remove unneeded characters
* Convert variable types

```{r}
# Remove trailing notes in Date variable
library(stringr)
my_table$Date <-  str_split_fixed(my_table$Date, "\\[", n = 2)[, 1]
my_table$`Per capita` <- gsub(",", "", my_table$`Per capita`)
head(my_table)
```

```{r message=FALSE}
my_table$`External debt` <- gsub(",", "", my_table$`External debt`)
my_table$`External debt` <-as.numeric(str_replace(my_table$`External debt`,"×10\\^", "e+"))
my_table$`Per capita` <- as.numeric(my_table$`Per capita`)
my_table$`% of GDP` <- as.numeric(my_table$`% of GDP`)
head(my_table)
```
```{r message=FALSE}
my_table$Date <- as.Date(my_table$Date,format = "%d %B %Y")
head(my_table)
```




